Entropy Rain: Dilution and Compression of Thermals in Stratified Domains

### 2019-07-24 tex/stratified_thermals.tex
adds Ben's updates

In the following sections, we will use the impulse of dense vortex rings to derive expressions for the evolution of their depth and radii with time.
\textbf{\citet{rast1998} showed that 2D compressible, low entropy plumes in stratified domains emit vortex pairs, and this description of vortex ring evolution should be useful both in our study of thermals and in more time-continuous plume sources.}

\begin{figure}[t!]
    \includegraphics[width=\columnwidth]{evolution_colormeshes.pdf}
    \caption{
	\textbf{Shown is the evolution of mass-weighted entropy perturbations, normalized by the thermal's buoyancy perturbation, from 3D simulations conducted in this work}.
	(left) A thermal in a weakly stratified domain with $N_\rho = 1/2$ density scale heights, and (right) a thermal in a strongly stratified domain with $N_\rho = 3$.
	While both start with precisely the same initial condition, the thermal in low stratification expands with depth \textbf{and slows down}, whereas the thermal in strong stratification compresses with depth \textbf{and accelerates}.
    \label{fig:evolution_colormeshes} }
\end{figure}

@@

We now restrict our study to an ideal gas in the low Mach-number regime, in an adiabatic background.
Due to rapid pressure equilibration in low Mach-number flows, we can approximate 
\begin{equation*}
\frac{\rho_1}{\rho_0} \approx -\frac{S_1}{c_P},
\end{equation*}
where $S_1$ is the specific entropy perturbation and $c_P$ is the specific heat at constant pressure; thermodynamic variables are decomposed into background (subscript 0) and fluctuating (subscript 1) components.

@@

Combining this with Eqn.~\ref{eqn:impulse_approx}, we retrieve our first main result,
\begin{equation}
r = \sqrt{\frac{\eta B_{\text{th}} (t + t_{\text{off}})}{\pi\rho_0\Gamma_{\text{th}}}}.
\label{eqn:r_theory}
\end{equation}
\textbf{$\Gamma_{\text{th}}$ is the characteristic circulation of the thermal. As} there are no net baroclinic torques, $\Gamma_{\text{th}}$ \textbf{remains nearly constant in our simulations} (Fig.~\ref{fig:constants}, middle panel).
In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in \LJ.
In the limit of strong stratification, we find $r \propto \rho^{-1/2}$, corresponding to purely horizontal compression, with $r^2 \propto \rho^{-1}$ \citep{brandenburg2016}.

To solve for the vertical evolution of the thermal, we can use Eqn.~\ref{eqn:momentum}.
We approximate the volume as $\mathcal{V} \approx m r^3$, where $m$ is a parameter which we take to be constant (which is a decent assumption \textbf{in our simulations}; see Fig.~\ref{fig:constants}, bottom panel).
\textbf{Here, $m$ accounts for volumetric constants, the aspect ratio of the thermal, and the ratio between the full radius of the spheroidal thermal and $r$, the radius to the entropy maxima.}
Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, we find
\begin{equation}
\frac{dz_{\text{th}}}{\rho(z_{\text{th}})^{1/2}} =
\left(\frac{(\pi\Gamma_{\text{th}})^{3/2}}{m(1 + k)(\eta B_{\text{th}})^{1/2}}\right)\frac{dt}{(t + t_{\text{off}})^{1/2}}.
\label{eqn:dz_theory}
\end{equation}
This can be easily integrated given an atmospheric stratification $\rho(z)$.

@@

We choose an atmospheric model in which the dynamic viscosity, $\mu = \rho_0 \nu$, and the thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform and constant in time.
We make this choice because $\mu$ and $\kappa$ appear in the density-weighted momentum and entropy equations, and we find the density-weighted entropy and momentum to be key quantities in our thermal theory.
The diffusivities $\nu$ and $\chi$ therefore scale inversely with the density.
As the diffusivities scale with depth, Re is specified at the thermal's initial depth.
All simulations conducted in this work use a value of Re = 600 and $\mbox{\text{Pr} = 1}$.

@@

For the fully compressible simulations, we must also specify the density perturbation $\rho_1$.
We pick perturbations that are in pressure equilibrium,
\begin{equation}
\ln\rho_1 = S_1/c_P, \qquad T_1 = T_0(e^{-\epsilon\ln\rho_1} - 1)/\epsilon.
\end{equation}

@@

\textbf{
In our 2D simulations, we represent the radial direction with Chebyshev polynomials so that we can include geometric factors in ours equations and capture the singularity at $r = 0$.
We then assume the z direction is periodic to make the calculations more efficient, and we end the simulations before the thermal can interact with the vertical periodic boundaries.
Remarkably, the results of these simulations vary only minimally from our 3D simulations, as we will show in the next section, indicating that the vertical periodicity and the different side boundaries (cylinder vs. cube) do not influcence the thermal properties.
}

@@

Finally, we quantify the excellent agreement between the 2D anelastic and 3D fully compressible simulations in Fig.~\ref{fig:diff}, bottom panel.
We ran simulations in both models for $N_\rho = [0.1, 0.5, 1, 2]$.
There are slight discrepancies early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the bottom of the domain.
Outside these times, we find differences in the radius of less than 1\%.
This gives us confidence that our high stratification anelastic simulations are producing reliable results.
\citet{lecoanet&all2014} also found close agreement between low Mach-number anelastic and fully compressible simulations.

\begin{deluxetable*}{c c c c c c c c}
\tabletypesize{\footnotesize}
\caption{Simulation output parameterization
\label{table:parameters}
}
\tablehead{																																															
\colhead{$N_\rho$} & \colhead{$z_{\text{th},0}$} & \colhead{$t_{\text{off}}$} & \colhead{$B_{\text{th}}$} & \colhead{$\Gamma_{\text{th}}$} & \colhead{$m$} & \colhead{$\eta$} & \colhead{$k$}	}	
\startdata																																															
\multicolumn{8}{l}{\textbf{2D Anelastic Simulations}}\\
0.1 	&  24.6 	& 0.144	& -0.548 & -2.17 & 8.05	& 1.04	& 0.732	\\
0.5 	&  24.2 	& 0.695	& -0.569 & -2.12 & 8.34	& 0.977	& 0.715	\\
1	 	&  23.7 	& 1.11 	& -0.602 & -2.05 & 8.65	& 0.915	& 0.703	\\
2	 	&  22.3 	& 1.27	& -0.713 & -1.89 & 9.23	& 0.842 & 0.682	\\
3	 	&  21.2 	& 1.01	& -0.947 & -1.73 & 9.81	& 0.807	& 0.654	\\
4	 	&  20.5 	& 0.615	& -1.47	 & -1.59 & 10.2	& 0.794	& 0.642	\\
5	 	&  20.0	    & 0.425	& -2.70	 & -1.49 & 10.7	& 0.781	& 0.609	\\
6	 	&  19.8 	& 0.041	& -5.73	 & -1.43 & 10.8	& 0.787	& 0.616	\\
\multicolumn{8}{l}{\textbf{3D Fully Compressible Simulations}}\\    
0.1 	&  23.4 	& -0.337& -0.547 & -2.17 & 8.98	& 1.06	& 0.636	\\
0.5 	&  23.8 	& 0.572	& -0.568 & -2.12 & 8.79	& 0.978	& 0.678	\\
1	 	&  23.6 	& 1.15	& -0.601 & -2.05 & 8.87	& 0.907	& 0.689	\\
2	 	&  22.4 	& 1.38	& -0.711 & -1.89 & 9.31	& 0.828	& 0.680	\\
\textbf{3}	 	&  \textbf{21.1} 	& \textbf{0.78}	& \textbf{-0.949} & \textbf{-1.75} & \textbf{9.99}	& \textbf{0.815}	& \textbf{0.648}	\\
\enddata																																															
\tablecomments{ 
Parameters presented in this table are best fits to simulation output data in the range $z = [0.1 L_z, 0.65 L_z]$.
Above this range, the thermal is still spinning up from initial conditions; below this range, 3D cases are heavily interacting with the bottom boundary.}
\end{deluxetable*}

The values of the parameters described in section \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
As anticipated, $\eta$ is $\mathcal{O}$(1) and decreases slightly in value with increasing stratification, consistent with Fig.~\ref{fig:constants}.
In all cases, the buoyancy $B_{\text{th}}$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
We also find that the non-dimensional circulation is $\mathcal{O}$(-2) for each of our cases, and decreases in magnitude with increasing stratification.

@@

We now estimate the behavior of thermals in the Sun based on the simulations presented in this work.
The thermal evolution depends on a variety of parameters (see table \ref{table:parameters}).
However, we find the only parameter which changes appreciably as we increase the stratification is the normalized buoyancy $B_\text{th}$.
To estimate $B_\text{th}$ in the sun, we approximate the dimensional buoyancy perturbation of Eqn.~\ref{eqn:tot_buoyancy} as $\tilde{B} = \rho \mathcal{V} g (S_1/c_p)$, and calculate this quantity for thermals launched from the solar photosphere, assuming that solar downflow lanes quickly break up into thermals.
Using the VAL atmospheric data of \citet{avrett&loeser2008}, we estimate the solar surface to have a temperature of $T_0 \approx 6000$ K, a density of $\rho_0 \approx 1.74 \times 10^{-7}$ g/cm$^3$, and a sound speed of $c_s = 9.5 \times 10^5$ cm/s.
We estimate that thermal diameters would be roughly the width of downflow lanes ($L_{\text{th}} = 0.1$ Mm), and the average atmospheric density over the first $L_{\text{th}}$ of the solar interior is $\bar{\rho} = 1.17\rho_0$.
Estimating downflows to have a temperature deviation of $T_1 = -500$ K \citep{borrero&bellotrubio2002}, the nondimensional entropy signature of solar downflows is $S_1/c_p \sim \gamma^{-1}\ln(1 + T_1/T_0) = -5.22 \times 10^{-2}$.
Using a solar surface gravity value of $g = 2.74 \times 10^4$ cm/s$^2$, the buoyancy of a spherical thermal is 
$$
\tilde{B} \approx \bar{\rho}\left[\frac{4\pi}{3} \left(\frac{L}{2}\right)^3\right] g \frac{S_1}{c_P} = -1.52 \times 10^{17} \text{g cm}^4/\text{s}^2.
$$
Nondimensionalizing this by $B_0 = (S_1/c_P) L^2 u_{\text{th}}^2 \rho_0$ with $u_{\text{th}} = c_s \sqrt{S_1/c_P}$, we find $B_\text{th} = \tilde{B}/B_0 = -3.57$, which lies between the $N_\rho = 5$ and $N_\rho = 6$ simulations we studied here (see table \ref{table:parameters}).

@@

We find that our estimated solar thermal is in the falling regime.
These thermals experience radial compression with corresponding increases in velocity, but experience much less compression than a naive approximation based on the density stratification alone.
\textbf{Interestingly, the thermal's Mach number is roughly a value of 0.1 throughout the full extent of the solar convection zone.}
Furthermore, throughout the thermal's fall, we find that $\tau_\kappa \gg \tau_{\text{ff}}$, and thus we do not expect the thermal to diffuse its entropic signature.
We find a fractional diffusion rate over the thermal's transit of the solar convection zone of 
$$
\int_{R_\odot}^{0.7 R_\odot} \tau_\kappa^{-1} \frac{dr}{w_{th}} = [6.55, 1.57]\times 10^{-3}\,\text{for}\,[B_\ell, B_u].
$$
Thus, the thermal loses less than 1\% of its entropic signature to diffusion.

\textbf{
We now briefly estimate the enthalpy flux carried by a thermal.
Following \citet{brandenburg2016}, we estimate the enthalpy flux of the thermal as $F_{\text{enth}} = \rho_0(z_th) T_0(z_th) w_{\text{th}} S_{1,\text{th}}$.
We estimate the thermal's entropic signature as $S_{1, th} = B_{\text{th}}/(\rho_0(z_{\text{th}}) V_{\text{th}} g/c_P)$, where the thermal volume is $V_{\text{th}} = m r_{\text{th}}^3$.
We take $\rho_0(z_{\text{th}})$, $T_0(z_{\text{th}})$, and $g/c_P$ from our solar MESA model at the depth of the thermal over its evolution.
We take $r_{\text{th}}$ and $w_{\text{th}}$ to be the thermal radius and velocity shown in the first and second panels of Fig.~\ref{fig:thermal_sun_comparison}.
We find $m$ from the data in Table \ref{table:parameters} in the same manner as we found $B_{\text{th}}$ for these solar thermals.
To estimate the total luminosity carried by one thermal, we calculate $L_{\text{enth, th}} = \pi r_{\text{th}}^2 F_{\text{enth}}$, and we plot this value as a function of depth, normalized by the solar luminosity, in panel 4 of Fig.~\ref{fig:thermal_sun_comparison}.
}

\textbf{
From our estimate of the luminosity carried by one thermal, we estimate the filling factor of downward propagating thermals required to carry the solar luminosity through their enthalpy flux.
We calculate $f_{\text{th}} = (L_{\odot}/L_{\text{enth, th}}) (\pi r_{\text{th}}^2)/(4\pi R^2)$, where $R$ is the thermal's radial distance form the center of the Sun.
We plot the $f_{\text{th}}$ in panel 5 of Fig.~\ref{fig:thermal_sun_comparison}.
The filling factor of thermals required to carry $L_\odot$ at the solar surface is greater than unity; this is unsurprising, as we know that solar surface convection carries the solar luminosity through the combined effects of upflows and downflows.
A few percentage of the solar radius beneath the photosphere, $f_{th}$ drops to a very modest $10^{-4}$, and by the base of the solar convection zone approaches $10^{-7}$.
These estimates suggest that even if a large fraction of the thermals launched from the solar surface break apart due to turbulence, this mechanism could still efficiently carry the solar luminosity deep in the convection zone.
}

\textbf{
While these estimates suggest that entropy rain could effectively transport the solar luminosity, we will briefly note that our handling of the enthalpy flux here ignores the contributions of the kinetic energy flux, potential energy flux, and viscous flux.
While we expect the last of these to be inconsequential, the kinetic energy flux (which transports luminosity inwards) and the potential energy flux (which transports luminosity outwards) may be large.
A more thorough examination of these fluxes are outside of the scope of this work, but due to the promising nature of our results found here for the entropy rain hypothesis, such work seems promising.
}

@@

\appendix
\section{Thermal Measurements}
\label{appendix:measurements}
Throughout this work, we frequently report the thermal's radius or its depth.
We measure the thermal's radius and height as the radius from the axis of symmetry and the height above $z = 0$ at which the thermal's vortex core is located.
We assume that the vortex core is located at the thermal's entropy minima.
To find the entropy minima vertically, we integrate $\int\rho S_1 r dr$ in our Dedalus domain, then use the spectral data of that profile to sample it on a 4096-point vertical grid; we take the location of the minima on that grid to be the thermal height.
To find the entropy minima horizontally, we integrate $\int \rho S_1 dz$ in our Dedalus domain, then sample the spectral data onto a 2048-point radial grid, and take the minima of that profile to be the radius of the thermal.
For our 2D simulations, we use entropy data from the full simulation domain to perform these calculations.
For our 3D simulations, we assume that the vortex ring is azimuthally symmetric, and thus use the entropy data in the $y = 0$ plane at radial values of $x \geq 0$.
In order to find the thermal's velocity as a function of time, we use a five-point stencil to differentiate the thermal's depth, $d_{\text{th}}$,
$$
w_{\text{th}}(t) = \frac{d }{dt}d_{\text{th}}(t) = \frac{-d_{\text{th}}(x + 2\Delta t) + 8d_{\text{th}}(t + \Delta t) - 8 d_{\text{th}}(t - \Delta t) + d_{\text{th}}(t - 2\Delta t)}{12\Delta t}
$$

@@

\section{Table of Simulations}
\label{appendix:table}
Information regarding the simulation resolution, evolution time, and CFL safety factor for each of the simulations presented in this work is contained in table \ref{table:simulation_info}.
The Python scripts used to perform all simulations and analysis in this work are stored online in a Zenodo repository \citep{supp_andersetall2019} \textbf{at \dataset[10.5281/zenodo.3311894]{https://doi.org/10.5281/zenodo.3311894}}.
\textbf{The 3D, $N_\rho = 3$ simulation displays spectral instabilities at very late times, affecting radial measurements at depths $\geq 17.5$.
We therefore truncate the data from that simulation at a depth of 15, which corresponds to multiple freefall times before these instabilities affect the solution.}

>>>>

In the following sections, we will use the impulse of dense vortex rings to derive expressions for the evolution of their depth and radii with time.
\textbf{In this work we study vortex rings generated by discrete cold thermals, but time-stationary cooling produces similar vortex ring structures \citep[as in e.g.,][]{rast1998}.
The following description of vortex ring evolution should therefore be broadly applicable.}

\begin{figure}[t!]
    \includegraphics[width=\columnwidth]{evolution_colormeshes.pdf}
    \caption{
	\textbf{Shown is the evolution of entropy perturbations, normalized by the thermal's buoyancy perturbation, from 3D simulations conducted in this work}.
	(left) A thermal in a weakly stratified domain with $N_\rho = 1/2$ density scale heights, and (right) a thermal in a strongly stratified domain with $N_\rho = 3$.
	While both start with precisely the same initial condition, the thermal in low stratification expands with depth \textbf{and slows down}, whereas the thermal in strong stratification compresses with depth \textbf{and accelerates}.
    \label{fig:evolution_colormeshes} }
\end{figure}

@@

We now restrict our study to an ideal gas in the low Mach-number regime, in an adiabatic background.
\textbf{Thi sis the appropriate regime of deep solar convection.}
Due to rapid pressure equilibration in low Mach-number flows, we can approximate 
\begin{equation*}
\frac{\rho_1}{\rho_0} \approx -\frac{S_1}{c_P},
\end{equation*}
where $S_1$ is the specific entropy perturbation and $c_P$ is the specific heat at constant pressure; thermodynamic variables are decomposed into background (subscript 0) and fluctuating (subscript 1) components.

@@

Combining this with Eqn.~\ref{eqn:impulse_approx}, we retrieve our first main result,
\begin{equation}
r = \sqrt{\frac{\eta B_{\text{th}} (t + t_{\text{off}})}{\pi\rho_0\Gamma_{\text{th}}}},
\label{eqn:r_theory}
\end{equation}
\textbf{Here, $\Gamma_{\text{th}}$ is the characteristic circulation of the thermal. As} there are no net baroclinic torques, $\Gamma_{\text{th}}$ \textbf{remains nearly constant in our simulations} (Fig.~\ref{fig:constants}, middle panel).
In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in \LJ.
In the limit of strong stratification, we find $r \propto \rho^{-1/2}$, corresponding to purely horizontal compression, with $r^2 \propto \rho^{-1}$ \citep{brandenburg2016}.

To solve for the vertical evolution of the thermal, we can use Eqn.~\ref{eqn:momentum}.
We approximate the volume as $\mathcal{V} \approx m r^3$, where $m$ is a parameter which we take to be constant (which is a decent assumption \textbf{in our simulations}; see Fig.~\ref{fig:constants}, bottom panel).
\textbf{Here, $m$ accounts for volumetric constants (e.g., $4\pi/3$), the aspect ratio of the thermal, and the cubed ratio between the full radius of the spheroidal thermal and $r$.}
Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, we find
\begin{equation}
\frac{dz_{\text{th}}}{\rho(z_{\text{th}})^{1/2}} =
\left(\frac{(\pi\Gamma_{\text{th}})^{3/2}}{m(1 + k)(\eta B_{\text{th}})^{1/2}}\right)\frac{dt}{(t + t_{\text{off}})^{1/2}}.
\label{eqn:dz_theory}
\end{equation}
This can be easily integrated given an atmospheric stratification $\rho(z)$.

@@

We choose an atmospheric model in which the dynamic viscosity, $\mu = \rho_0 \nu$, and the thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform \textbf{in space} and constant in time.
We make this choice because $\mu$ and $\kappa$ appear in the density-weighted momentum and entropy equations, and we find the density-weighted entropy and momentum to be key quantities in our thermal theory.
The diffusivities $\nu$ and $\chi$ therefore scale inversely with the density.
As the diffusivities scale with depth, Re is specified at the thermal's initial depth.
All simulations conducted in this work use \textbf{an initial} value of Re = 600 and $\mbox{\text{Pr} = 1}$.

@@

For the fully compressible simulations, we must also specify the density perturbation $\rho_1$.
We pick perturbations that are in pressure equilibrium,
\begin{equation}
\ln\rho_1 = S_1/c_P, \qquad T_1 = T_0(e^{-\epsilon\ln\rho_1} - 1)/\epsilon.
\end{equation}
\textbf{In all cases, we do not add any symmetry breaking perturbations (e.g., noise).}

@@

\textbf{
In our 2D simulations, we represent the radial direction with Chebyshev polynomials so that we can include geometric factors in our equations and capture the singularity at $r = 0$.
We then assume the z direction is periodic to make the calculations more efficient, and we end the simulations before the thermal can interact with the vertical periodic boundaries.
Remarkably, the results of these simulations vary only minimally from our 3D simulations, as we will show in the next section, indicating that the vertical periodicity and the different side boundaries (cylinder vs. cube) do not influcence the thermal properties.
}

@@

Finally, we quantify the excellent agreement between the 2D anelastic and 3D fully compressible simulations in Fig.~\ref{fig:diff}, bottom panel.
We ran simulations in both models for $N_\rho = [0.1, 0.5, 1, 2, 3]$.
There are slight discrepancies early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the bottom of the domain.
Outside these times, we find differences in the \textbf{measured} radius of less than 1\%.
This gives us confidence that our high stratification anelastic simulations are producing reliable results.
\citet{lecoanet&all2014} also found close agreement between low Mach-number anelastic and fully compressible simulations.

\begin{deluxetable*}{c c c c c c c c}
\tabletypesize{\footnotesize}
\caption{Simulation output parameterization
\label{table:parameters}
}
\tablehead{																																															
\colhead{$N_\rho$} & \colhead{$z_{\text{th},0}$} & \colhead{$t_{\text{off}}$} & \colhead{$B_{\text{th}}$} & \colhead{$\Gamma_{\text{th}}$} & \colhead{$m$} & \colhead{$\eta$} & \colhead{$k$}	}	
\startdata																																															
\multicolumn{8}{l}{\textbf{2D Anelastic Simulations (Cylindrical)}}\\
0.1 	&  24.6 	& 0.144	& -0.548 & -2.17 & 8.05	& 1.04	& 0.732	\\
0.5 	&  24.2 	& 0.695	& -0.569 & -2.12 & 8.34	& 0.977	& 0.715	\\
1	 	&  23.7 	& 1.11 	& -0.602 & -2.05 & 8.65	& 0.915	& 0.703	\\
2	 	&  22.3 	& 1.27	& -0.713 & -1.89 & 9.23	& 0.842 & 0.682	\\
3	 	&  21.2 	& 1.01	& -0.947 & -1.73 & 9.81	& 0.807	& 0.654	\\
4	 	&  20.5 	& 0.615	& -1.47	 & -1.59 & 10.2	& 0.794	& 0.642	\\
5	 	&  20.0	    & 0.425	& -2.70	 & -1.49 & 10.7	& 0.781	& 0.609	\\
6	 	&  19.8 	& 0.041	& -5.73	 & -1.43 & 10.8	& 0.787	& 0.616	\\
\multicolumn{8}{l}{\textbf{3D Fully Compressible Simulations (Cartesian)}}\\    
0.1 	&  23.4 	& -0.337& -0.547 & -2.17 & 8.98	& 1.06	& 0.636	\\
0.5 	&  23.8 	& 0.572	& -0.568 & -2.12 & 8.79	& 0.978	& 0.678	\\
1	 	&  23.6 	& 1.15	& -0.601 & -2.05 & 8.87	& 0.907	& 0.689	\\
2	 	&  22.4 	& 1.38	& -0.711 & -1.89 & 9.31	& 0.828	& 0.680	\\
\textbf{3}	 	&  \textbf{21.1} 	& \textbf{0.78}	& \textbf{-0.949} & \textbf{-1.75} & \textbf{9.99}	& \textbf{0.815}	& \textbf{0.648}	\\
\enddata																																															
\tablecomments{ 
Parameters presented in this table are best fits to simulation output data in the range $z = [0.1 L_z, 0.65 L_z]$.
Above this range, the thermal is still spinning up from initial conditions; below this range, 3D cases are heavily interacting with the bottom boundary.}
\end{deluxetable*}

The values of the parameters described in section \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
As anticipated, $\eta$ is $\mathcal{O}$(1) and decreases slightly in value with increasing stratification, consistent with Fig.~\ref{fig:constants}.
In all cases, the buoyancy $B_{\text{th}}$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
We also find that the non-dimensional circulation is \textbf{roughly} $-2$ for each of our cases, and decreases in magnitude with increasing stratification.

@@

We now estimate the behavior of thermals in the Sun based on the simulations presented in this work.
The thermal evolution depends on a variety of parameters (see table \ref{table:parameters}).
However, we find the only parameter which changes appreciably as we increase the stratification is the normalized buoyancy $B_\text{th}$.
To estimate $B_\text{th}$ in the sun, we approximate the dimensional buoyancy perturbation of Eqn.~\ref{eqn:tot_buoyancy} as $\tilde{B} = \rho \mathcal{V} g (S_1/c_p)$, and calculate this quantity for thermals launched from the solar photosphere, assuming that solar downflow lanes quickly break up into thermals.
Using the VAL atmospheric data of \citet{avrett&loeser2008}, we estimate the solar surface to have a temperature of $T_0 \approx 6000$ K, a density of $\rho_0 \approx 1.74 \times 10^{-7}$ g/cm$^3$, and a sound speed of $c_s = 9.5 \times 10^5$ cm/s.
We estimate that thermal diameters would be roughly the width of downflow lanes ($L_{\text{th}} = 0.1$ Mm), and the average atmospheric density over the first $L_{\text{th}}$ of the solar interior is $\bar{\rho} = 1.17\rho_0$.
Estimating downflows to have a temperature deviation of $T_1 = -500$ K \citep{borrero&bellotrubio2002}, the nondimensional entropy signature of solar downflows is $S_1/c_p \sim \gamma^{-1}\ln(1 + T_1/T_0) = -5.22 \times 10^{-2}$.
Using a solar surface gravity value of $g = 2.74 \times 10^4$ cm/s$^2$ \textbf{and assuming thermal formation occurs at the solar photosphere}, the buoyancy of a spherical thermal is 
$$
\tilde{B} \approx \bar{\rho}\left[\frac{4\pi}{3} \left(\frac{L}{2}\right)^3\right] g \frac{S_1}{c_P} = -1.52 \times 10^{17} \text{g cm}^4/\text{s}^2.
$$
Nondimensionalizing this by $B_0 = (S_1/c_P) L^2 u_{\text{th}}^2 \rho_0$ with $u_{\text{th}} = c_s \sqrt{S_1/c_P}$, we find $B_\text{th} = \tilde{B}/B_0 = -3.57$, which lies between the $N_\rho = 5$ and $N_\rho = 6$ simulations we studied here (see table \ref{table:parameters}).

@@

We find that our estimated solar thermal is \textbf{likely} in the falling regime.
These thermals experience radial compression with corresponding increases in velocity, but experience much less compression than a naive approximation based on the density stratification alone.
\textbf{Interestingly, the thermal's Mach number is roughly a value of 0.1 throughout the full extent of the solar convection zone.}
Furthermore, throughout the thermal's fall, we find that $\tau_\kappa \gg \tau_{\text{ff}}$, and thus we do not expect the thermal to diffuse its entropic signature.
We find a fractional diffusion rate over the thermal's transit of the solar convection zone of 
$$
\int_{R_\odot}^{0.7 R_\odot} \tau_\kappa^{-1} \frac{dr}{w_{th}} = [6.55, 1.57]\times 10^{-3}\,\text{for}\,[B_\ell, B_u].
$$
Thus, the thermal loses less than 1\% of its entropic signature to diffusion.

\textbf{
We now briefly estimate the enthalpy flux carried by a thermal.
Following \citet{brandenburg2016}, we estimate the enthalpy flux of the thermal as $F_{\text{enth}} = \rho_0(z_{\text{th}}) T_0(z_{\text{th}}) w_{\text{th}} S_{1,\text{th}}$.
We estimate the thermal's entropic signature as $S_{1, \text{th}} = B_{\text{th}}/(\rho_0(z_{\text{th}}) V_{\text{th}} g/c_P)$, where the thermal volume is $V_{\text{th}} = m r_{\text{th}}^3$.
We take $\rho_0(z_{\text{th}})$, $T_0(z_{\text{th}})$, and $g/c_P$ from our solar MESA model at the depth of the thermal over its evolution.
We take $r_{\text{th}}$ and $w_{\text{th}}$ to be the thermal radius and velocity shown in the first and second panels of Fig.~\ref{fig:thermal_sun_comparison}.
We find $m$ from the data in Table \ref{table:parameters} in the same manner as we found $B_{\text{th}}$ for these solar thermals.
To estimate the total luminosity carried by one thermal, we calculate $L_{\text{enth, th}} = \pi r_{\text{th}}^2 F_{\text{enth}}$, and we plot this value as a function of depth, normalized by the solar luminosity, in the fourth panel of Fig.~\ref{fig:thermal_sun_comparison}.
}

\textbf{
From this estimate of the luminosity carried by one thermal, we now calulate the filling factor of downward propagating thermals required to carry the solar luminosity.
We calculate $f_{\text{th}} = [(L_{\odot}/L_{\text{enth, th}}) (\pi r_{\text{th}}^2)]/(4\pi R^2)$, where $R$ is the thermal's radial distance from the center of the Sun.
Panel 5 of Fig.~\ref{fig:thermal_sun_comparison} displays $f_{\text{th}}$ vs.~depth.
The filling factor of thermals required to carry $L_\odot$ at the solar surface is greater than unity; this is unsurprising, as we know that solar surface convection carries the solar luminosity through the combined effects of upflows and downflows.
A few percentage of the solar radius beneath the photosphere, $f_{\text{th}}$ drops to a very modest $10^{-4}$, and by the base of the solar convection zone approaches $10^{-7}$.
These estimates suggest that even if a large fraction of the thermals launched from the solar surface break apart due to turbulence, entropy rain could still efficiently carry the solar luminosity deep in the convection zone.
}

\textbf{
We briefly note that our handling of the enthalpy flux here ignores the contributions of the kinetic energy flux, potential energy flux, and viscous flux.
While we expect the last of these to be inconsequential, the kinetic energy flux (which transports luminosity inwards) and the potential energy flux (which transports luminosity outwards) may be large.
We encourage future work to examine these fluxes more thoroughly, but such an examination is outside of the scope of this work.
}

@@

\appendix
\section{Thermal Measurements}
\label{appendix:measurements}
Throughout this work, we frequently report the thermal's radius or its height.
We measure the thermal's radius and height as the radius from the axis of symmetry and the height above $z = 0$ at which the thermal's vortex core is located.
We assume that the vortex core is located at the thermal's entropy minima.
To find the entropy minima vertically, we integrate $\int\rho S_1 r dr$ in our Dedalus domain, then use the spectral data of that profile to sample it on a 4096-point vertical grid; we take the location of the minima on that grid to be the thermal height.
To find the entropy minima horizontally, we integrate $\int \rho S_1 dz$ in our Dedalus domain, then sample the spectral data onto a 2048-point radial grid, and take the minima of that profile to be the radius of the thermal.
For our 2D simulations, we use entropy data from the full simulation domain to perform these calculations.
For our 3D simulations, we assume that the vortex ring is azimuthally symmetric, and thus use the entropy data in the $y = 0$ plane at radial values of $x \geq 0$.
In order to find the thermal's velocity as a function of time, we use a five-point stencil to differentiate the thermal's depth, $d_{\text{th}}$,
$$
w_{\text{th}}(t) = \frac{d }{dt}d_{\text{th}}(t) = \frac{-d_{\text{th}}(x + 2\Delta t) + 8d_{\text{th}}(t + \Delta t) - 8 d_{\text{th}}(t - \Delta t) + d_{\text{th}}(t - 2\Delta t)}{12\Delta t}
$$

@@

\section{Table of Simulations}
\label{appendix:table}
Information regarding the simulation resolution, evolution time, and CFL safety factor for each of the simulations presented in this work is contained in table \ref{table:simulation_info}.
The Python scripts used to perform all simulations and analysis in this work are stored online in a Zenodo repository \citep{supp_andersetall2019} \textbf{at \dataset[10.5281/zenodo.3311894]{https://doi.org/10.5281/zenodo.3311894}}.
\textbf{The 3D, $N_\rho = 3$ simulation displays spectral instabilities at very late times as the simulation is under-resolved at these times.
This affects thermal radial measurements at depths $\geq 17.5$.
We therefore truncate the data from that simulation at a depth of 15, which corresponds to multiple freefall times before these instabilities affect the solution.}

\begin{deluxetable*}{c c c c c }
\tabletypesize{\footnotesize}
\caption{Table of simulation information
\label{table:simulation_info}
}
\tablehead{																																															
\colhead{$N_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{\text{evolution}}$} & \colhead{safety}	}	
\startdata																																															
\multicolumn{5}{l}{\textbf{2D Anelastic Simulations}}\\
0.1 	& 		128			& 512			& 50 	&	0.6	\\
0.5 	& 		128			& 512			& 45 	&	0.6	\\
1	 	& 		128			& 512			& 41 	&	0.6	\\
2	 	& 		128			& 1024			& 34	&	0.4	\\
3	 	& 		192			& 1024			& 29	&	0.4	\\
4	 	& 		256			& 1024			& 26 	&	0.3	\\
5	 	& 		256			& 1536			& 25 	&	0.14	\\
6	 	& 		256			& 1536			& 23 	&	0.08	\\
\multicolumn{5}{l}{\textbf{3D Fully Compressible Simulations}}\\
0.1 	& 		256			& 512			& 50 		&	0.15	\\
0.5 	& 		256			& 512			& 45 		&	0.15	\\
1	 	& 		256			& 512			& 41	 	&	0.15	\\
2	 	& 		\textbf{384}			& 1024			& 34    	&	0.1	\\
\textbf{3}	 	& 		\textbf{384}			& \textbf{2048}			& \textbf{25}    	&	\textbf{0.15}	\\
\enddata																																															
\tablecomments{
Our 2D cylindrical sims have spectral mode resolution of nr x nz, and our 3D cartesian sims have spectral mode resolution of nx x ny x nz.
We evolve our simulations from initial conditions until $t_{\text{evolution}}$ dimensionless freefall times have passed.
We use a CFL to determine the appropriate size of our timestep at each timestep in our simulation, and the CFL safety factor decreases with increasing stratification.
Our 2D sims use the RK443 timestepper and our 3D sims use the SBDF2 timestepper, resulting in different safety factor sizes in 2D and 3D.
}
\end{deluxetable*}
